
\section{Feasibility}
This study is made to see if the project on completion will serve the purpose of the organization for the
amount of work, effort and the time that spend on it. Feasibility study lets the developer foresee the future
of the project and the usefulness.\\\\
A feasibility study is designed to provide an overview of the primary issues related to a business idea. The
purpose is to identify any make or break issues that would prevent your business from being successful
in the marketplace.\\\\
The objective of the feasibility study is to establish the reasons for developing the software that is accept-
able to users, adaptable to change and conformable to established standards.\\

\subsection{Technical Feasibility}
SamanyaSeva is technically feasible as it is built up using various open source technologies and can run on any platform.

\subsection{Economical Feasibility}
Since the system will be developed as part of project work, there will be no manual cost to spend for the proposed system. Also all the resources are already available, it gives an indication that the application is economically possible for development.

 %In other words, a feasibility study determines whether the business idea makes sense.
%A thorough feasibility analysis provides a lot of information necessary for the business plan. For example, a good market analysis is necessary in order to determine the project's feasibility. This information
%provides the basis for the market section of the business plan.\\\\
%The objective of the feasibility study is to establish the reasons for developing the software that is accept-
%able to users, adaptable to change and conformable to established standards.\\
%Carrying out a feasibility study involves information assessment, information collection and report writing.


\section{Need and Significance}
\begin{itemize}
	\item Better customer satisfaction.
	\item Improved supplier Performance.
	\item Improved Resource Utility.
	\end{itemize}

