\begin{Large}
\centertext{User Manual}
\end{Large}
It could also deal with CSV Format. CSV(Character Separated File) is a simple file format used to store tabular data, such as a
spreadsheet or database. Files in the CSV format can be imported to and exported from programs
that store data in tables, such as Microsoft Excel or OpenOffice CAs the Name "Certificate Generation System" Implies this application is used to 
generate certificate in an automated manner in few steps: 
\begin{enumerate}
\item Select Design from the images shown on the first page.
   (Put mouse pointer over the image to see larger view.)
\item Next Page will be page for entering College Details.
\begin{itemize}
\item Fill in the details of institution for which the certificate(s) is to be made.
\item Place mouse pointer over Input box te see an example for that input.
\end{itemize}
\item Next page will show two options
\begin{itemize}
\item Manual Entry    -> Select it for Generating Certificate for Single candidate.
\item Upload Csv File -> Select it for Generating certificate for more than 1 candidate by providing their details in Csv file.
\end{itemize}
\end{enumerate}

\begin{Large}
\centertext{Procedure}
\end{Large}
\textbf{\emph{Manual Filling}}
\begin{itemize}
\item On Selecting Manual Entry Next page will open containing input boxes for candidate Details.
\item Enter the details and select the image also.
\end{itemize}
Also by clicking on "Generate Another Ceritificate" you can generate another certificate with same design \& institute details and different Candidate Details.
And by clicking on "Goto First Page" you can again start from Design Selection Page.\\\\
\textbf{\emph{Csv Format}}
\begin{enumerate}
\item On selecting 'Upload csv File' Next page will open containing the conditions for the files to be uploaded for certificate generation.
\item A sample file can be downloaded from the link provided in the 'Note' in the instructions on page.
\item Sample file is a zip file named sample.zip containing the csv file and .zip file for images.
\item Extract it and then sample certificates can be produced using 'sample.csv' and 'images.zip' files.
\item That's it your certificate file is produced for all the candidates provided in the csv data file.
\end{enumerate}  
\begin{Large}
\centertext{Download}
\end{Large}    
The final result i.e Certificate can be saved in more than one format:
\begin{itemize}
\item pdf (portable document format)
\item Any other format eg. odt etc.
\end{itemize}


