\section{Overview}
\subsection{What is Octave?}
Octave is an open-source interactive software system for numerical computations and
graphics. It is particularly designed for matrix computations: solving simultaneous equations, computing eigenvectors and eigenvalues and so on. In many real-world engineering
problems the data can be expressed as matrices and vectors, and boil down to these forms
of solution.\\\\
In addition, Octave can display data in a variety of different ways, and it
also has its own programming language which allows the system to be extended. It can
be thought of as a very powerful, programmable, graphical calculator.\\
Octave makes it easy to solve a wide range of numerical problems, allowing you to spend more time
experimenting and thinking about the wider problem.
Octave was originally developed as a companion software to undergraduate course
book on chemical reactor design.\\
 It is currently being developed under the leadership of
Dr. J.W. Eaton and released under the GNU General Public Licence. Octave’s usefulness
is enhanced in that it is mostly syntax compatible with MATLAB which is commonly used
in industry and academics.
\subsection{ What Octave is not?}
Octave is designed to solve mathematical problems
numerically, that is by calculating values in the computer's memory. This means that it can't always give an exact solution
to a problem, and it should not be confused with programs such as Mathematica or Maple, which give symbolic
solutions by doing the algebraic manipulation. \\
This does not make it better or worse, its just used for different tasks. Most real mathematical problems
(particularly engineering ones!) do not have neat symbolic solutions.
\subsection{ Who uses Octave?}
Octave and MATLAB are widely used by engineers and scientists, in both industry and
academia for performing numerical computations, and for developing and testing mathematical algorithms.\\
 For example, NASA use it to develop spacecraft docking systems;
\begin{itemize}
\item Jaguar Racing use it to display and analyse data transmitted from their Formula 1 cars.
\item Sheffield University use it to develop software to recognise cancerous cells. 
\item It makes it very easy to write mathematical programs quickly, and display data in a wide range of
different ways.
\end{itemize}
\subsection{Why not use a ‘normal’ highlevel language, e.g. C++ ?}
C++ and other industry-standard programming languages are normally designed for writing general-purpose software. However, solutions to mathematical problems take time to
program using C++, and the language does not natively support many mathematical concepts, or displaying graphics.\\
Octave is specially designed to solve these kind of problems,
perform calculations, and display the results. 

\section{The Existing System}
There are few existing systems for solving this particular problem like Sage or other softwares but
they don’t have following features required by our mentor. These system were not open source
and free web based software that were need.
All exiting system suffers from at least one of the following system.
 \subsection{Limitations of previous system }
\begin{itemize}
\item No batch mode. 

\item Don't give output as png images.

\item They are costly.

\item They don't save output.

\item They need installation and a lot of system resources. 

\item They don't save user session.

\item Earlier it was on CGI, now moved to PHP. 
\end{itemize}
\subsection{Advantages of shifting the system from CGI to PHP:}
\begin{itemize}
\item PHP was specially designed for a websites, the facilities that web designers typically want in a scripting language are built into it.
\item Another convenience is its handling of form input.
\item Accessing databases is just as easy. There are built-in facilities in PHP to access MySQL, Dbase, Oracle, InterBase, and so on.
\item Need to MIME encode your message? There's a function to do it for you too.
\item When PHP scripts runs, If in case  you get error then messages will be like pinpointing the offending lines in your code to help you locate the error.
\end{itemize} 
\section{User Requirement Analysis}
\begin{enumerate}
\item Perform most of difficult Calculation work.
\item Make it work like batch mode. so, that user can give inputs 
together and relax.
\item Help M.Tech and Civil Engineer to analysis structure.
\item Automatic calculation of modal force and modes.
\item Reduce the time for analysis.
\item Provide on-line way to analysis so that individual does not have to 
install anything.
\end{enumerate}



