
\section{Problem Formulation}
It can be hectic sometimes to write each and everything and thus, most of the people go for shortcuts. Even many students see this as waste of time which strictly it's not, as it can be a major help in long run. That's the reason many big companies maintain their blogs to attract crowd, to advertise the product and to keep a track on the things done.
\noindent Hence, I came up with a solution to add speech-recognision module in this system which can reduce efforts of the users in writing. I also provided a direct method to save the content in pdf form for printing purporse.

\section{Facilities required for proposed work}
\subsection{Hardware Requirements}
\begin{itemize}
\item Operating System: Linux/Windows
\item Processor Speed: 512KHz or more
\item RAM: Minimum 256MB
\end{itemize}
\subsection{Software Requirements}
\begin{itemize}
\item Software: Mysql Database system
\item Programming Language: PHP, Web development languages (HTML,CSS and JS)
\end{itemize}

\section{Methodology}
\begin{itemize}
\item A secure login method for users.
\item Space to enter content. (text or speech)
\item Admin can create users to give access in a private firm.
\item Everything will be saved side by side in a database.
\item Generate PDF document.
\end{itemize}

\section{Project Work} 
\textbf{Studied Previous System:}\\
Before starting the project. \\\\
\textbf{Learn Languages:}\\
Before starting with project, we have to go through the basics of Web Development languages and PHP, Mysql, such that there should not be any problem proceeding with project.\\\\
\textbf{Get Familiar with Bootstrap:}\\
Bootstrap will make the project responsive and also provides various means through which implementation becomes easier.\\\\
\textbf{Users:}\\
Limited users can be given access of the system in a private firm and can even see a list of users with their\\\\
\textbf{Posts:}\\
User can add content through text or speech and can get a PDF document of the same. All the published posts will be seen on web module of the system.\\\\
\textbf{Contact:}\\
Contact details page has been made for any kind of suggestions or problems. You just have to drop a mail.\\\\
\textbf{Output:}\\
The CMS will manage and save your content for future reference and provide a method to edit the published content too.
